Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme

### 2013-06-18 Report/article.tex
Present

\subsection{Cost of the Cryptosystem}
 In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time. These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem. The measurements in this section were taken on M2. From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$. Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation. The same thing happend to \texttt{Encrypt} which evaluate a polynomial of bigger degree. And as for the rest of function they depend on the size of ciphertext which become bigger because $p$ become bigger.

>>>>

\subsection{Cost of the Cryptosystem}
 In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time. These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem. The measurements in this section were taken on M2. From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$. Futhermore, we observe that the size of the public key is increasing with $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the degree which makes the prime number $p$ difficult to be found and hence it increases the duration of key generation. The reasoning extends to \texttt{Encrypt} which evaluates a polynomial of higher degree. As for the rest of functions they depend on the size of ciphertext which becomes bigger with $p$.
